---
title  : "Assessment Tree"
author : "Klinkenberg"
date   : "4/6/2017"
output : html_document
---

```{r setup, include=FALSE}
# Install the following three packages if not available.

if(!"collapsibleTree" %in% installed.packages()) { install.packages("collapsibleTree") };
if(!"data.tree"       %in% installed.packages()) { install.packages("data.tree")       };
if(!"readxl"          %in% installed.packages()) { install.packages("readxl")          };
library("collapsibleTree")
library("readxl")
library("data.tree")
```

Assessment decision tree for tool selection based on answer types. Select the item type you want to use and find out what kind of assessment application to use.

```{r, echo=FALSE}
# Read .xlsx file
assessment.tree <- read_excel("assessment_tree.xlsx")

# Create tree
collapsibleTree(assessment.tree,
                root      = "Question Type",        # Specify root name. This can be any string
                hierarchy = names(assessment.tree), # Use column headers from .xlsx file as branches
                width     = 800,                    # Set width in pixels
                fontSize  = 14                      # Set font size
               )
```

Here the application categories are:

* Generic assessment tool (e.g. QMP, Remindo, TestVision)
* Grading tool for written assignments (e.g. TurnitIn, GradeWorks)
* Parameterised assessment tool (e.g. MapleTA, SOWISO)
* LMS (Blackboard, Canvas)